---
title: "Syuzeth Library"
output: html_document
---

Sentiment analysis is here done through the use of R package "Syuzhet" developed by Mattew Jockers at the Nebraska Literary Lab documentation is available at [Syuzeth github repository](https://github.com/mjockers/syuzhet).

#### **What is Syuzhet?**

Syuzhet is one of the two terms describing a narrative composition, along with the fabula, theorized by Russian Formalists Victor Shklovsky and Vladimir Propp. It refers to the "device" or technique of a narrative and is concerned with the manner in which the components of a story are organized. \n

Since the object of our study is a collection of movies, rich of narrative expedients that do not follow a chronological order, such as flashbacks, we needed a method of analysis that would also take into consideration this specificity for a better understanding of the emotions in the plot.

```{r}
library(syuzhet)
result_list <- list()
```

First we import the Syuzhet package a variable for storing our resulting vector in a list

```{r echo=TRUE, warning=FALSE}
setwd("~/Desktop/cartoonlp/txts")
x<- list.files()
for (film in x) {
  dir = paste("~/Desktop/cartoonlp/txts/",film, sep="" )
  text <- file(description=film, open = "r")
  film_as_string<- get_text_as_string(text)
  s_v <- get_sentences(film_as_string)
  sentiment <- get_sentiment(s_v)
  result_list <- append(result_list, list(sentiment))
}

```

With a for() function we analyse each file contained in the "/txts" directory.

A result list containing nested lists, containing values representing each sentence analysed using the syuzhet default method, is created
